---
title: "Assignment 3.2"
subtitle: "CPSC 292 Section -- (Waldrop)"
author: "Borey Kong"
date: "10/28/2022"
output: html_notebook
---

## Assignment 3.2 

```{r, include=TRUE}
# Loading required libraries

```

### Question 1

*Complete the following steps:*

 a. *Generate 10 random, whole numbers using `sample()` and store them in a vector named `hop`.*

```{r, include=TRUE}
hop <- sample(c(1:100), size= 10, replace=T)
```
 
 b.  *Create a function that will take a single number \verb+x+ and return the results of the following calculation: $2x^2 -3x +12$*

```{r, include=TRUE}
questionb <- function(x) { 
  a <- (2*x^2) - (3*x) + 12
  return(a)
}

questionb(5)
```

 c. *Use your function to calculate the result of each element of `hop` individually. Store the result in a new vector called `hop.up1`.  Note: you must do this to each of the ten elements individually. Hint: create `hop.up1` first as a vector of `NA`'s. *
 
```{r, include=TRUE}
hop.up1 <- rep(NA, length = 10)

hop.up1 <- c(
  questionb(hop[1]),
  questionb(hop[2]),
  questionb(hop[3]),
  questionb(hop[4]),
  questionb(hop[5]),
  questionb(hop[6]),
  questionb(hop[7]),
  questionb(hop[8]),
  questionb(hop[9]),
  questionb(hop[10])
  )
hop.up1
```

 d. *Now use your function to perform a vectorized calculation of the equation on `hop` and store this as `hop.up2`.*
 
```{r, include=TRUE}
hop.up2 <- questionb(hop)
hop.up2
```

 e.  *Last, use `all.equal()` to test whether or not `hop.up1` and `hop.up2` are the same. (They should be!)*
 
```{r, include=TRUE}
all.equal(hop.up1, hop.up2)
```

### Question 2

*Make a function that reports the data in `state.x77` (in `data("state")`) for a specific state defined by the user.*

```{r, include=TRUE}
data("state")

whatstate <- function(x){
  a <- state.x77[x, ]
  return(a)
}

whatstate("Washington")

```