---
title: "Assignment 2.1"
subtitle: "CPSC 292 Section -- (Waldrop)"
author: "Borey Kong"
date: "10/05/2022"
output: html_notebook
---

## Assignment 2.1

```{r, include=TRUE}
# Loading required libraries

```

### Question 1

*Load the pressure data set. Make a plot of vapor pressure in mmHg versus temperature in C of mercury. Set the axis labels and title. Make the same plot using a different method (either with or without a formula).*

Plot without a formula: 
```{r, include=TRUE}
data("pressure")
pressure
pressure.temperature <- c(pressure$temperature)
pressure.pressure <- c(pressure$pressure)
plot(pressure.temperature,pressure.pressure,
     ylab = "Vapor Pressure (mmHg)",
     xlab = "Temperature in C of mercury",
     main = "Vapor Pressure versus Temperature")

```

Plot with a formula: 
```{r, include=TRUE}
plot(pressure ~ temperature, data=pressure,
     ylab = "Vapor Pressure",
     xlab= "Temperature",
     main= "Vapor Pressure versus Temperature 2")

```


### Question 2

*Load the dataset Loblolly. Make a plot of height versus age of trees where data are triangle-shaped points. Color the points according to the seed number.*

```{r, include=TRUE}
data("Loblolly")
seedcolors <- c("red","orange","yellow","green","blue","purple","pink","brown","black","white")

plot(height ~ age, data=Loblolly,
     ylab= "Height", xlab= "Age",
     col= seedcolors[Loblolly$Seed],
     pch= rep(24,10)[Loblolly$Seed])
```